The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-12 thesis/paper.tex
Comments

%Structure of the paper
The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study. Section \ref{case_company_description} describes the case company and the API which was studied. A description of our methodology is introduced in Section \ref{methodology}. In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the findings of our study. In Section \ref{conclusion} we propose the potential impact of our work and give suggestions for future work that builds on our research.

\section{Background} \label{existing_literature}
This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study. Follow that, we will introduce the company and API examined in this study.

>>>>

%Structure of the paper
The sections following the Introduction are structured as follows: In Section \ref{background}, we present the background and previously published work that is related to our study. Section \ref{case_company_description} describes the case company and the API which was studied. A description of our methodology is introduced in Section \ref{methodology}. In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the findings of our study. In Section \ref{conclusion} we propose the potential impact of our work and give suggestions for future work that builds on our research.

\section{Background} \label{background}
This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study. Follow that, we will introduce the company and API examined in this study.
